Factor Analysis on Citations, Using a Combined Latent and Logistic Regression Model

### 2019-10-03 Manuscript for submission/manuscript.tex
Update

\begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:Modified}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of the log-likelihood function is bounded away from zero ($\tau > 0$):
\[
\nabla^{2}h(\Theta) = \mbox{diag}\Big(\mbox{vec}\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
\]
For any vector $a$, $\mbox{diag}(a)$ is the diagonal matrix with elements of $a$ on its diagonal.
For any matrix $B=[b_1,\dots,b_n]\in\mathbb{R}^{n \times n}$, $\mbox{vec}(B)\in\mathbb{R}^{n^2}$ is obtained by stacking $ b_1,\dots, b_{n}$ in order.
For any square matrix $A$ and $B$, we have $ A \succcurlyeq B $ if and only if matrix $A-B$ is positive semi-definite.
\end{assumption}

@@

With these assumptions, we present the behavior of non-asymptotic error bound of our estimator through the following theorem. In our result, we measure error using squared Frobenius norm summed across three matrices:
\[
    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})
    :=\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F}^{2} + \|\widehat{\Delta}^{L}\|_{F}^{2} + \|\widehat{\Delta}^{S}\|_{F}^{2}
\]

\begin{theorem} \label{Th:th1}
Under the assumptions \ref{Ass:1} and \ref{Ass:2},
if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
\begin{align} \label{eq:49}
\delta \geq 2\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 2\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
\end{align}
then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
\begin{align}
    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}},
\end{align}
where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
\end{theorem}

We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension to Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
Our work considers a logistic loss function whose parameters are characterized by a sparse matrix plus a low rank matrix, whereas Agarwal, et al.\cite{agarwal2012noisy} work on a quadratic loss of a noisy realization of a linear transformation of sum of a low rank matrix and a sparse matrix.
We show that similar proof techniques can be applied in our case, giving us similar results.
%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.

Result of the Theorem \ref{Th:th1} provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $M$, and rank parameter $k$, helping us to understand the behavior of our proposed estimator both in practice and in ideal cases. In real-world, large scale citation network analysis, it is difficult to expect network with $L^*$ matrix with exactly $k(\ll n)$ non-zero eigenvalues, but with a matrix $L^*$ with approximately low rank.
In this case, our theorem provides the intuition on the rate on how fast the error bound $\mathcal{K}_{L^*}$ will grow.
In ideal cases where $L^*$ is an exact low rank matrix with rank $k$ (i.e., $rank(L^*)=k$) and $S^*$ is a sparse matrix, which lies within model subspace $M$ (i.e., $|supp(S^*)|=s$), we can easily verify ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ (i.e., $\tau\sum_{j=k+1}^{n}\sigma_j(L^*)$) and in $\mathcal{K}_{S^*}$ (i.e., $\tau\sum_{(i,j)\notin M}|S_{ij}^*|$) disappear, giving us Frobenius error bound as follows:
\[
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s
\]
where $\lesssim$ denotes that we ignore constant factors.

@@

We now present each of the three steps of the ADMM algorithm and show that the proximal
operators $\mathbf{P}_{\lambda,f}$ and $\mathbf{P}_{\lambda,g}$ are easy to evaluate.
Let
$$
x^m = (x^m_\alpha, x^m_M, x^m_L, x^m_S), \quad
z^m = (z^m_\alpha, z^m_M, z^m_L, z^m_S), \quad
u^m = (u^m_\alpha, u^m_M, u^m_L, u^m_S).
$$
Step 1. We solve $x^{m+1} = \mathbf{P}_{\lambda,f}(z^m - u^m)$.
Due to the special structure of $f(\cdot)$,
$x^{m+1}_\alpha, x^{m+1}_M, x^{m+1}_L$, and $x^{m+1}_S$
can be updated separately.
More precisely, we have
\begin{eqnarray}
x^{m+1}_\alpha, x^{m+1}_M &=& \mbox{arg min}_{\alpha, M} \quad
-\frac{\alpha}{n} \sum_{1\le i< j\le n}X_{ij}
-\frac{1}{2n} X \bullet M
+ \frac{1}{n} \sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + M_{ij}}\right) \nonumber \\
&& + \frac{1}{2\lambda}\left[\alpha - (z^m_\alpha - u^m_\alpha)\right]^2
+ \frac{1}{2\lambda}\|M - (z^m_M - u^m_M)\|^2_F, \label{eq:admm02} \\
x^{m+1}_L &=& \mbox{arg min}_{ L} \quad \delta \|L\|_\ast
+ \frac{1}{2\lambda}\|L - (z^m_L - u^m_L)\|^2_F,\label{eq:admm03}
\\
&& \mbox{subject to $L$ is positive semidefinite;} \nonumber \\
x^{m+1}_S &=& \mbox{arg min}_{ S} \quad  \gamma \|S\|_1
+ \frac{1}{2\lambda}\|S - (z^m_S - u^m_S)\|^2_F,
\label{eq:admm04}
\\
&& \mbox{subject to $S$ is symmetric,} \nonumber
\end{eqnarray}
where $\|\cdot\|_F$ is the matrix Frobenius norm, defined as
$\|M\|^2_F = \sum_{i,j} m^2_{ij}$ for a matrix $M = (m_{ij})$.
The problem in \eqref{eq:admm02} may not have a closed-form solution.
We use a simple gradient descent to solve in this step, setting the step size equal to $0.05$ and stopping criteria as $\max(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}) \leq 10^{-9}$.
Note that there are close-form solutions to \eqref{eq:admm03} and \eqref{eq:admm04}, while \eqref{eq:admm02} is a unconstrained convex optimization problem.
More specifically, in \eqref{eq:admm03}, suppose the eigenvalue decomposition of the symmetric matrix $(z^m_L - u^m_L)$ can be written as
$$
z^m_L - u^m_L = T \Lambda T^T,
$$
where $T$ is orthogonal ($T T^T = I_n$). Then, for $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, we have
$$
x^{m+1}_L = J (T \mbox{diag}(\Lambda-\lambda \delta)_+ T^T)J^{T},
$$
and diag$(\Lambda-\lambda \delta)_+$ is a diagonal matrix with the $j$th
diagonal entry being
$$
(\Lambda_{jj}-\lambda \delta)_+ = \left\{
\begin{array}{ll}
0, & \mbox{ if } \Lambda_{jj} < \lambda \delta, \\
\Lambda_{jj}-\lambda \delta, & \mbox{ if } \Lambda_{jj} \ge \lambda \delta .
\end{array}
\right.
$$
In \eqref{eq:admm04}, we have, for $i \neq j$,
\[
S_{ij} = \left\{
\begin{array}{ll}
0, & \mbox{ if } |(z^m_S - u^m_S)_{ij}| < \lambda \gamma,  \\
(z^m_S - u^m_S)_{ij}-\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} > \lambda \gamma, \\
(z^m_S - u^m_S)_{ij}+\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} <- \lambda \gamma.
\end{array}
\right.
\]

@@

    \item Recall that the binary factor loading matrix $F^*$ encodes the relation between topics and papers
        (i.e., if $i$th paper studies about $k$th topic, we denote $F^*_{ki}=1$, otherwise $F^*_{ki}=0$).
        First, we assume that there are $n$ papers in the network, and $K$ topics are embedded in the network. Each of them consists of $\frac{n}{K}$ papers.
        This can be expressed in $F^*$ as follows:
        \[
            F^* =
               \begin{bmatrix}
                 \smash[b]{\block{n/K}} \\
                 && \smash[b]{\block{n/K}} \\
                 &&&& \ddots \\
                 &&&&& \block{n/K}
                \end{bmatrix}
              \in R^{K \times n},
        \]
        where each row of $F^*$ has $\frac{n}{K}$ $1$'s and each column has only one $1$.
        Then, we assume that $n_{l}$ papers share $l$ topics and $n_{m}$ papers share $m$ topics ($1 < l < m \leq K$).
        This can be represented in the $F^*$ in following steps:
        $1)$ Pick distinct $n_{l}$ indices randomly from $\{1,2,\dots,n\}$.
        We will denote the set of the indices as $\Omega_{n_l}$.
        $2)$ Choose $n_{m}$ indices from the set $\{1,2,\dots,n\}\setminus \Omega_{n_{l}}$ and denote the set of those indices as $\Omega_{n_{m}}$.
        $3)$ Make the columns of $F^*$ with corresponding indices in set $\Omega_{n_{l}} \cup \Omega_{n_{m}}$ zeros.
        $4)$ We use a notation $f^*_j$ to denote the $j$th column of the matrix $F^*$.
        Fill arbitrary $l$ entries of $f^*_j$ for $j \in \Omega_{n_l}$ with $1$s, and also fill arbitrary $m$ entries of $f^*_j$ for $j \in \Omega_{n_m}$ with $1$s.
        Lastly, we set $F^*=JF^*$ where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$.

@@

    \item Remind that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
        In the spirit of this notion, we construct ad-hoc links in a way that they connect the clusters of papers with one topic.
        Specifically, we assume that there are $\frac{|S^*|}{_KC_{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
        This can be implemented via following steps:
        1) We construct $K$ sets $C^*_1,\dots,C^*_K$ that are defined as follows:
        \begin{align*}
           &C^*_{1} \subseteq \big\{1, 2, \dots, \frac{n}{K} \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\} \\
           &C^*_{2} \subseteq \big\{\frac{n}{K}+1, \dots, \frac{2n}{K} \big\} \setminus \big\{ \Omega_{n_l} \cup \Omega_{n_m} \big\}  \\
           &\vdots \\
           &C^*_{K} \subseteq \big\{\frac{(K-1)n}{K}+1, \dots, n \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\}
        \end{align*}
        where each of them has arbitrary $\frac{|S^*|}{_KC_{2}}$ elements.
        2) Create a set $I_{S^*}$ whose elements are pairs of indices such that
        \[
            I_{S^*} =
            \bigg\{ (i_r,j_r) : i_r \in C^*_p, j_r \in C^*_q, 1 \leq p < q \leq K,   r = 1,2,\dots,\frac{|S^*|}{_KC_{2}} \bigg\},
        \]
        where we use $i_r$ to indicate $r$th element $i$ in the set.
        3) Draw $S^*_{ij} \sim \mbox{Unif}[19,20], \forall (i,j) \in I_{S^*}$.
        4) Lastly, make it symmetric by setting $S^*_{jj}=S^*_{ij},\forall 1\leq i < j \leq n$.
    \item Create an upper-triangular part of the adjacency matrix $X$ whose each entry $X_{ij}$ follows Bernoulli distribution.
        The distribution's parameter is parametrized by a probability, $P^{*}_{ij}=\frac{\exp (\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}$.
        After drawing all the entries of $X$ in the upper-triangular part, then make the matrix symmetric by setting $X_{ji}=X_{ij},\forall 1 \leq i < j \leq n$.
\end{enumerate}

@@

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig1.pdf}
\caption{Graphical illustrations of six synthetic networks.
Nodes that share the common factors are clustered. The cross cluster links are ad-hoc Citations.}
\label{fig:figure1}
\end{figure}

@@

    \begin{table}[htbp]
    \centering
    \begin{tabular}{c|ccc|ccc|ccc}
                & \multicolumn{9}{c}{\textbf{Scenario 1}}                                              \\
                \cline{2-10}
                & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\
                \cline{2-10}
                & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
                \hline
    $M_{1}$   &    1 (3)  &    0 (2)   &  0 (2)  &    1 (4)    &  0 (3)   &  0 (3)  &    1 (5)  &   0 (4)    & 0 (4) \\
    $M_{2}$   &    1     &    0 &      0 &         1    &     1  &    1  &         1    &    1   &   1   \\
    $M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
    $M_{4}$   &  0  &   $\frac{20}{30}$    &  $\frac{20}{30}$    &   0          &   $\frac{25}{40}$    &   $\frac{25}{30}$   &  0      &  $\frac{30}{30}$     &   $\frac{30}{30}$   \\
                \hline
    \end{tabular}

>>>>

\begin{assumption}(\textbf{Strong convexity})  \label{Ass:1}
For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:Modified}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of the log-likelihood function is bounded away from zero ($\tau > 0$):
\[
\nabla^{2}h(\Theta) = \mbox{diag}\Big(\mbox{vec}\Big(\frac{1}{n}\frac{\exp(\Theta)}{(1+\exp(\Theta))^{2}}
\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
\]
For any vector $a$, $\mbox{diag}(a)$ is the diagonal matrix with elements of $a$ on its diagonal.
For any matrix $B=[b_1,\dots,b_n]\in\mathbb{R}^{n \times n}$, $\mbox{vec}(B)\in\mathbb{R}^{n^2}$ is obtained by stacking $ b_1,\dots, b_{n}$ in order.
For any square matrix $A$ and $B$, we have $ A \succcurlyeq B $ if and only if matrix $A-B$ is positive semi-definite.
\end{assumption}

@@

With these assumptions, we present the behavior of non-asymptotic error bound of our estimator through the following theorem. In our result, we measure error using squared Frobenius norm summed across three matrices:
\[
    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})
    :=\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F}^{2} + \left\|\widehat{\Delta}^{L}\right\|_{F}^{2} + \left\|\widehat{\Delta}^{S}\right\|_{F}^{2}
\]

\begin{theorem} \label{Th:th1}
Under the assumptions \ref{Ass:1} and \ref{Ass:2},
if we solve the convex problem (\ref{eq:Modified}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
\begin{align} \label{eq:49}
\delta \geq 2 \left\|\frac{1}{n}(X-P^{*}) \right\|_{op} \quad and \quad \gamma \geq 2\left\|\frac{1}{n}(X-P^{*})\right\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg),
\end{align}
then there exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$, and $s = 1,2,...,n^{2}$, and we have the following upper bound on $e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S})$
\begin{align} \label{theorem1}
    e^{2}(\widehat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \leq
    \underbrace{c_{1}\frac{\delta^{2}}{\tau^{2}}}
    _{\mathcal{K}_{\alpha^*}} +
    \underbrace{c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\}}_{\mathcal{K}_{L^*}} +
    \underbrace{c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\sum_{(i,j) \notin M}|S^*_{ij}|\bigg\}}_{\mathcal{K}_{S^*}},
\end{align}
where $M$ is an arbitrary subset of matrix indices of cardinality at most s.
\end{theorem}

We would first like to note that the result presented in Theorem \ref{Th:th1} can be thought of as an extension of Theorem $1$ presented in paper \cite{agarwal2012noisy} to a generalized linear model.
Specifically, our work considers a logistic loss function whose parameter is characterized by a sparse matrix plus a low rank matrix,
whereas Agarwal, et al.\cite{agarwal2012noisy} work on a general linear observation model whose parameter is also 
characterized by sum of a low rank matrix and a sparse matrix.

%In this Section, we show that similar proof techniques can be applied in our case, giving us similar results.
%Detailed descriptions of each terms in bound are elaborated in paper \cite{agarwal2012noisy}.

Astute readers might have noticed that the upper bound in \ref{theorem1} consists of three different terms, where we denote them as
$\mathcal{K}_{\alpha^*}$, $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$. 
Each respective term is involved with estimating three model parameters, $\alpha, L$ and $S$.
To be more specific, both $\mathcal{K}_{L^*}$ and $\mathcal{K}_{S^*}$ have two types of error:
1) The first one is called as an ``estimation error''. 
This error represents the statistical cost of estimating parameters which belong to the model subspace. 
2) Another quantity is referred as ``approximation error''. 
This error occurs when we only focus on estimating parameters within the model subspace, 
and it shrinks as the model subspace becomes large.
%=\left\|\widehat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F}^{2} + \left\|\widehat{\Delta}^{L}\right\|_{F}^{2} + \left\|\widehat{\Delta}^{S}\right\|_{F}^{2}

The result of the Theorem \ref{Th:th1} provides a family of upper-bounds, one for each indexed by a specific choice of model subspace $M$, and rank parameter $k$.
In other words, this means that the subset $M$ and the target rank $k$ can be adaptively chosen so as to obtain the tightest upper bound.
In ideal case where $L^*$ is an exact low rank matrix with rank $k$ \big(i.e., $\mbox{rank}(L^*)=k$\big) and $S^*$ is a sparse matrix, whose support lies within the model subspace $M$ \big(i.e., $\mbox{supp}(S^*) \subset M$\big), we can easily see ``\emph{approximation error}'' terms in $\mathcal{K}_{L^*}$ \big(i.e., $\delta\sum_{j=k+1}^{n}\sigma_j(L^*)$ \big) and in $\mathcal{K}_{S^*}$ \big(i.e., $\gamma\sum_{(i,j)\notin M}|S_{ij}^*|$\big) disappear, giving us Frobenius error bound as follows:
\[
    e^{2}(\hat{\alpha}\mathbbm{1}\mathbbm{1}^T,\widehat{L},\widehat{S}) \lesssim \delta^2(k+1)+\gamma^2s.
\]
Here we use the notation $X \lesssim Y$ to denote that there exists universal absolute constant $C$ such that $X \leq CY$.

%This helps us to understand the behavior of our proposed estimator both in practice and in ideal cases. In real-world, large scale citation network analysis, it is difficult to expect network with $L^*$ matrix with exactly $k(\ll n)$ non-zero eigenvalues, but with a matrix $L^*$ with approximately low rank.

@@

We now present each of the three steps of the ADMM algorithm and show that the proximal
operators $\mathbf{P}_{\lambda,f}$ and $\mathbf{P}_{\lambda,g}$ are easy to evaluate.
Let
$$
x^m = (x^m_\alpha, x^m_M, x^m_L, x^m_S), \quad
z^m = (z^m_\alpha, z^m_M, z^m_L, z^m_S), \quad
u^m = (u^m_\alpha, u^m_M, u^m_L, u^m_S).
$$
Step 1. We solve $x^{m+1} = \mathbf{P}_{\lambda,f}(z^m - u^m)$.
Due to the special structure of $f(\cdot)$,
$x^{m+1}_\alpha, x^{m+1}_M, x^{m+1}_L$, and $x^{m+1}_S$
can be updated separately.
More precisely, we have
\begin{eqnarray}
x^{m+1}_\alpha, x^{m+1}_M &=& \mbox{arg min}_{\alpha, M} \quad
-\frac{\alpha}{n} \sum_{1\le i< j\le n}X_{ij}
-\frac{1}{2n} X \bullet M
+ \frac{1}{n} \sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + M_{ij}}\right) \nonumber \\
&& + \frac{1}{2\lambda}\left[\alpha - (z^m_\alpha - u^m_\alpha)\right]^2
+ \frac{1}{2\lambda}\|M - (z^m_M - u^m_M)\|^2_F, \label{eq:admm02} \\
x^{m+1}_L &=& \mbox{arg min}_{ L} \quad \delta \|L\|_\ast
+ \frac{1}{2\lambda}\|L - (z^m_L - u^m_L)\|^2_F,\label{eq:admm03}
\\
&& \mbox{subject to $L$ is positive semidefinite;} \nonumber \\
x^{m+1}_S &=& \mbox{arg min}_{ S} \quad  \gamma \|S\|_1
+ \frac{1}{2\lambda}\|S - (z^m_S - u^m_S)\|^2_F,
\label{eq:admm04}
\\
&& \mbox{subject to $S$ is symmetric,} \nonumber
\end{eqnarray}
where $\|\cdot\|_F$ is the matrix Frobenius norm, defined as
$\|M\|^2_F = \sum_{i,j} m^2_{ij}$ for a matrix $M = \{(m_{ij})\}_{i,j=1}^{n}$.
The problem in \eqref{eq:admm02} may not have a closed-form solution.
We use a simple gradient descent to solve in this step, setting the step size equal to $0.05$ and stopping criteria as $\max\big(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}\big) \leq 10^{-9}$.
Note that there are close-form solutions to \eqref{eq:admm03} and \eqref{eq:admm04}, while \eqref{eq:admm02} is a unconstrained convex optimization problem.
More specifically, in \eqref{eq:admm03}, suppose the eigenvalue decomposition of the symmetric matrix $(z^m_L - u^m_L)$ can be written as
$$
z^m_L - u^m_L = T \Lambda T^T,
$$
where $T$ is orthogonal ($T T^T = I_n$). Then, for $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, we have
$$
x^{m+1}_L = J \big(T \mbox{diag}(\Lambda-\lambda \delta\big)_+ T^T)J^{T},
$$
and diag$(\Lambda-\lambda \delta)_+$ is a diagonal matrix with the $j$th
diagonal entry being
$$
(\Lambda_{jj}-\lambda \delta)_+ = \left\{
\begin{array}{ll}
0, & \mbox{ if } \Lambda_{jj} < \lambda \delta, \\
\Lambda_{jj}-\lambda \delta, & \mbox{ if } \Lambda_{jj} \ge \lambda \delta .
\end{array}
\right.
$$
In \eqref{eq:admm04}, we have, for $i \neq j$,
\[
S_{ij} = \left\{
\begin{array}{ll}
0, & \mbox{ if } |(z^m_S - u^m_S)_{ij}| < \lambda \gamma,  \\
(z^m_S - u^m_S)_{ij}-\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} > \lambda \gamma, \\
(z^m_S - u^m_S)_{ij}+\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} <- \lambda \gamma.
\end{array}
\right.
\]

@@

    \item Recall that the binary factor loading matrix $F^*$ encodes the relation between topics and papers
        (i.e., if $i$th paper studies about $k$th topic, we denote $F^*_{ki}=1$, otherwise $F^*_{ki}=0$).
        First, we assume that there are $n$ papers in the network, and $K$ topics are embedded in it. 
        Each of them consists of $\frac{n}{K}$ papers.
        This can be expressed in $F^*$ as follows:
        \[
            F^* =
               \begin{bmatrix}
                 \smash[b]{\block{n/K}} \\
                 && \smash[b]{\block{n/K}} \\
                 &&&& \ddots \\
                 &&&&& \block{n/K}
                \end{bmatrix}
              \in R^{K \times n},
        \]
        where each row of $F^*$ has $\frac{n}{K}$ $1$'s and each column has only one $1$.
        Then, we assume that $n_{l}$ papers share $l$ topics and $n_{m}$ papers share $m$ topics ($1 < l < m \leq K$).
        This can be represented in the $F^*$ in following steps:
        $1)$ Pick distinct $n_{l}$ indices randomly from $\{1,2,\dots,n\}$.
        We will denote the set of the indices as $\Omega_{n_l}$.
        $2)$ Choose $n_{m}$ indices from the set $\{1,2,\dots,n\}\setminus \Omega_{n_{l}}$ and denote the set of those indices as $\Omega_{n_{m}}$.
        $3)$ Make the columns of $F^*$ with corresponding indices in set $\Omega_{n_{l}} \cup \Omega_{n_{m}}$ zeros.
        $4)$ We use a notation $f^*_j$ to denote the $j$th column of the matrix $F^*$.
        Fill arbitrary $l$ entries of $f^*_j$ for $j \in \Omega_{n_l}$ with $1$s, and also fill arbitrary $m$ entries of $f^*_j$ for $j \in \Omega_{n_m}$ with $1$s.
        Lastly, we set $F^*=JF^*$ where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$.

@@

    \item Remind that the positive entries of $S^*$ can characterize the links in the network which cannot be accounted by the common topics.
        In the spirit of this notion, we construct ad-hoc links in a way that they connect the clusters of papers with one topic.
        Specifically, we assume that there are $\frac{|S^*|}{_KC_{2}}$ edges between two clusters, where $|S^*|$ denotes the number of non-zero entries of the upper-triangular part of the matrix $S^*$.
        This can be implemented via following steps:
        1) We construct $K$ sets $C^*_1,\dots,C^*_K$ that are defined as follows:
        \begin{align*}
           &C^*_{1} \subseteq \big\{1, 2, \dots, \frac{n}{K} \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\} \\
           &C^*_{2} \subseteq \big\{\frac{n}{K}+1, \dots, \frac{2n}{K} \big\} \setminus \big\{ \Omega_{n_l} \cup \Omega_{n_m} \big\}  \\
           &\vdots \\
           &C^*_{K} \subseteq \big\{\frac{(K-1)n}{K}+1, \dots, n \big\} \setminus \big\{ \Omega_{n_l}
           \cup \Omega_{n_m} \big\}
        \end{align*}
        where each of them has arbitrary $\frac{|S^*|}{_KC_{2}}$ elements.
        2) Create a set $I_{S^*}$ whose elements are pairs of indices such that
        \[
            I_{S^*} =
            \bigg\{ (i_r,j_r) : i_r \in C^*_p, j_r \in C^*_q, 1 \leq p < q \leq K,   r = 1,2,\dots,\frac{|S^*|}{_KC_{2}} \bigg\},
        \]
        where we use $i_r$ to indicate $r$th element $i$ in the set.
        3) Draw $S^*_{ij} \sim \mbox{Unif}[19,20], \forall (i,j) \in I_{S^*}$.
        4) Lastly, make it symmetric by setting $S^*_{ji}=S^*_{ij},\forall 1\leq i < j \leq n$.
    \item Create an upper-triangular part of the adjacency matrix $X$ whose each entry $X_{ij}$ follows Bernoulli distribution.
        The distribution's parameter is parametrized by a probability, $P^{*}_{ij}=\frac{\exp (\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}{1+\exp(\alpha^{*}+f^{*T}_{i}D^{*}f^{*}_{j} +  S^{*}_{ij})}$.
        After drawing all the entries of $X$ in the upper-triangular part, then make the matrix symmetric by setting $X_{ji}=X_{ij},\forall 1 \leq i < j \leq n$.
\end{enumerate}

@@

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig1.pdf}
\caption{Graphical illustrations of six synthetic networks.
Nodes that share the common factors are clustered. The cross cluster links are ad-hoc Citations.
All the graphs are drawn via R package `igraph'.}
\label{fig:figure1}
\end{figure}

@@

    \begin{table}[htbp]
    \centering
    \begin{tabular}{c|ccc|ccc|ccc}
                & \multicolumn{9}{c}{\textbf{Scenario 1}}                                              \\
                \cline{2-10}
                & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\
                \cline{2-10}
                & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
                \hline
    $M_{1}$   &    1 (3)  &    0 (2)   &  0 (2)  &    1 (4)    &  0 (3)   &  0 (3)  &    1 (5)  &   0 (4)    & 0 (4) \\
    $M_{2}$   &    1     &    0 &      0 &         1    &     1  &    1  &         1    &    1   &   1   \\
    $M_{3}$   &    0     &    0 &      0 &         0    &     0  &    0  &         0    &    0   &   0   \\
    $M_{4}$   &  0  &   $\frac{10}{30}$    &  $\frac{10}{30}$    &   0          &   $\frac{20}{80}$    &   $\frac{20}{80}$   &  0      &  $\frac{24}{120}$     &   $\frac{24}{120}$   \\
                \hline
    \end{tabular}

    \begin{tabular}{c|ccc|ccc|ccc}
                & \multicolumn{9}{c}{\textbf{Scenario 2}}                                              \\
                \cline{2-10}
                & \multicolumn{3}{c|}{Case 4} & \multicolumn{3}{c|}{Case 5} & \multicolumn{3}{c}{Case 6} \\
                \cline{2-10}
                & Heuristic   & AIC   & BIC  &    Heuristic   & AIC   & BIC  & Heuristic   & AIC   & BIC  \\
                \hline
    $M_{1}$   &   1 (3)     &     1 (3)  &  1 (3)    &      1 (3)   &   1 (3)    &  1 (3)    &   1 (3)     &  1 (3)   & 1 (3)   \\
    $M_{2}$   &   $\frac{17}{18}$   &   0    &    0  &   $\frac{17}{18}$     &   0    &  0    &  $\frac{16}{18}$    &   0    &  0    \\
    $M_{3}$   &   0 &     0  &   0   &        0     &    0   &  0    &        0     &   0    & 0 \\
    $M_{4}$   &  0  &   0    &  0    &   0          &   0    &   0   &  0      &  0     &   0   \\
                \hline
    \end{tabular}
    \caption{ For two scenarios, our heuristic method chooses the model with $\widehat{L}$ with true rank, $\widehat{S}$ whose $M_2$ value is close to $1$, and $M_3$ value is close to $0$.
    Also note that it chooses a model whose mis-classification rate is close to $0$.
    A number in the parentheses represents the rank of $\widehat{L}$ estimated from ($\gamma^{\text{Heu}},\delta^{\text{Heu}}$), ($\gamma^{\text{AIC}},\delta^{\text{AIC}}$) and ($\gamma^{\text{BIC}},\delta^{\text{BIC}}$) for each case.}
    \label{tab:table1}
    \end{table}
